Survey paper tables and figures

### 2021-10-29 survey/code/paper-tables.Rmd

ggplot(to_plot, aes(x = time_value, y = value, color = REGION)) +
  geom_line() +
  facet_wrap(vars(signal), nrow = 2, ncol = 3, scales = "free_y") +
  labs(x = "Date", y = "", color = "Census Region") +
  scale_x_date(date_breaks = "3 months",
               date_labels = "%b %Y",
               date_minor_breaks = "1 month",
               guide = guide_axis(angle = 45)) +
  scale_y_continuous(minor_breaks = NULL) +
  theme_bw() +
  theme(legend.position = "bottom",
        strip.background = element_rect(color = "black", fill = "white"))

@@

```{r case-rate-compare-plot}
g <- ggplot(state_case_compare) +
  facet_geo(~ state_abbr, grid = "us_state_grid1", label = "code") +
  geom_line(aes(x = week, y = case_rate_adult, color = "Surveillance"),
            linetype = 1, size = 0.5) +
  geom_line(aes(x = week, y = ever_pos, color = "CTIS"),
            linetype = 1, size = 0.5) +
  scale_color_manual(values = c("lightblue", "gray50")) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 10, 20),
                     minor_breaks = c(5, 15),
                     labels = label_percent(scale = 1,
                                            accuracy = 1)) +
  scale_x_date(breaks = as.Date(c("2020-10-01", "2021-04-01")),
               date_labels = "%b", minor_breaks = NULL) +
  labs(x = "", y = "", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text = element_text(size = rel(0.5)))

>>>>

ggplot(to_plot, aes(x = time_value, y = value, color = REGION)) +
  geom_line() +
  facet_wrap(vars(signal), nrow = 2, ncol = 3, scales = "free_y") +
  labs(x = "Date", y = "", color = "Census region") +
  scale_x_date(date_breaks = "3 months",
               date_labels = "%b %Y",
               date_minor_breaks = "1 month",
               guide = guide_axis(angle = 45)) +
  scale_y_continuous(minor_breaks = NULL) +
  theme_bw() +
  theme(legend.position = "bottom",
        strip.background = element_rect(color = "black", fill = "white"))

@@

```{r case-rate-compare-plot}
g <- ggplot(state_case_compare) +
  facet_geo(~ state_abbr, grid = "us_state_grid1", label = "code") +
  geom_line(aes(x = week, y = case_rate_adult, color = "Surveillance"),
            linetype = 1, size = 0.5) +
  geom_line(aes(x = week, y = ever_pos, color = "CTIS"),
            linetype = 1, size = 0.5) +
  scale_color_manual(values = c("steelblue", "black")) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 10, 20),
                     minor_breaks = c(5, 15),
                     labels = label_percent(scale = 1,
                                            accuracy = 1)) +
  scale_x_date(breaks = as.Date(c("2020-10-01", "2021-04-01")),
               date_labels = "%b", minor_breaks = NULL) +
  labs(x = "", y = "", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text = element_text(size = rel(0.5)))
